\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{comment}
\usepackage{float}
\usepackage{cite}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath,amssymb,amsfonts}
% \usepackage{algorithmic}
\usepackage[dvipdfmx]{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage[T1]{fontenc}
\usepackage{mdframed}
\usepackage{algorithm, algpseudocode} % texlive-science
\usepackage[braket, qm]{qcircuit}


\usepackage[braket, qm]{qcircuit}
\usepackage{tikz}
%
%\input{img/defs}
%\usepackage{floatrow}

\usepackage{master_thesis}
%\usepackage{ascmac}
\usepackage{siunitx}
\usepackage{enumerate}

\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\algrenewcommand\algorithmicindent{0.5em}%
\makeatletter
\newcommand{\sublabel}[1]{\protected@edef\@currentlabel{\thefigure(\thesubfigure)}\label{#1}}
\makeatother
\newcommand{\thickhline}{%
    \noalign {\ifnum 0=`}\fi \hrule height 1pt
    \futurelet \reserved@a \@xhline
}
%% \def\thickhline{%
%%   \noalign{\ifnum0=`}\fi\hrule \@height \thickarrayrulewidth \futurelet
%%   \reserved@a\@xthickhline}

%% \def\hlinewd#1{%
%% \noalign{\ifnum0=`}\fi\hrule \@height #1 %
%% \futurelet\reserved@a\@xhline}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\renewcommand{\baselinestretch}{1.08}
%\makeatletter
\newcommand{\figcaption}[1]{\def\@captype{figure}\caption{#1}}
\newcommand{\tblcaption}[1]{\def\@captype{table}\caption{#1}}
%\makeatother

\begin{document}

\title{Improving T-depth Management in MCT Gate Decomposition}
\author{\IEEEauthorblockN{1\textsuperscript{st} David Clarino}
  \IEEEauthorblockA{\textit{Graduate School of} \\
    \textit{Information Science and Engineering} \\
    \textit{Ritsumeikan University}\\
    Kusatsu, Japan \\
    dizzy@ngc.is.ritsumei.ac.jp}
  \and
  \IEEEauthorblockN{2\textsuperscript{nd} Kouki Hirono}
  \IEEEauthorblockA{\textit{Graduate School of } \\
    \textit{Information Science and Engineering} \\
    \textit{Ritsumeikan University}\\
    Kusatsu, Japan \\
    accel@ngc.is.ritsumei.ac.jp}
  \and
  \IEEEauthorblockN{3\textsuperscript{rd} Shigeru Yamashita}
  \IEEEauthorblockA{\textit{Graduate School of} \\
    \textit{ Information Science and Engineering} \\
    \textit{Ritsumeikan University}\\
    Kusatsu, Japan\\
    ger@ngc.is.ritsumei.ac.jp}
}

\maketitle

\begin{abstract}

  In quantum circuit design, it is very important to reduce the T-depth. Decomposition
  methods of Multiple Controlled Toffoli (MCT) gates that reduce the T-depth have been
  researched. In existing decomposition methods of MCT gates, the T-depth of MCT gates
  is reduced by devising the decomposition. When decomposing multiple MCT gates,
  differences in the T-depth for each bit occur. Existing decomposition methods of MCT
  gates do not consider the T-depth for each bit, so existing decomposition methods of
  MCT gates may not be optimal. In this paper, we propose a method to reduce the T-depth
  by decomposing MCT gates while considering the T-depth for each bit. In the proposed
  method, bits with small T-depth are used preferentially, and the T-depth is reduced
  by decomposing MCT gates. In addition, the T-depth of the entire circuit is reduced
  by determining the decomposition of MCT gates while considering the subsequent gates.
  We confirmed that the proposed method can reduce the T-depth by an average of 17.1\%
  compared to existing methods. 
\end{abstract}

\begin{IEEEkeywords}
relative-phase Toffoli gates (RTOF), circuit optimization, LUT, synthesis
\end{IEEEkeywords}


\input{Intro.tex}
\input{Pre.tex}
%% \input{Mot.tex}
\input{Pro.tex}
%% \input{Exp.tex}
%% \input{Concl.tex}

%\renewcommand{\baselinestretch}{1.2}
\vspace{-0.3cm}
%\renewcommand{\baselinestretch}{1.0}
\bibliographystyle{plain}
\bibliography{ref}
%\vspace{12pt}
\end{document}
